
---
title: "A/B Testing Analysis: E-Commerce Landing Page Redesign"
author: "Chanya Trakulmaykee"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(broom)
```

## 🎯 Project Objective

Determine if a new landing page version leads to a significantly higher user conversion rate than the old page.

## 📂 Load the Dataset

```{r load-data}
ab_data <- read.csv("~/Downloads/ab_data.csv")
head(ab_data)
str(ab_data)
summary(ab_data)
```

## 🧼 Data Cleaning

Check for inconsistencies: users appearing in both groups or mismatched landing pages.

```{r clean-data}
# Check if landing page and group match
ab_data_clean <- ab_data %>%
  filter((group == "control" & landing_page == "old_page") |
         (group == "treatment" & landing_page == "new_page"))

# Remove duplicate users
ab_data_clean <- ab_data_clean[!duplicated(ab_data_clean$user_id), ]
```

## 📊 Conversion Rate Comparison

```{r conversion-rates}
ab_data_clean %>%
  group_by(group) %>%
  summarise(conversion_rate = mean(converted))
```

## 📈 Visualization

```{r conversion-plot}
ab_data_clean %>%
  group_by(group) %>%
  summarise(conversion_rate = mean(converted)) %>%
  ggplot(aes(x = group, y = conversion_rate, fill = group)) +
  geom_col(width = 0.6) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Conversion Rate by Group", x = "", y = "Conversion Rate") +
  theme_minimal()
```

## 📐 Hypothesis Testing

- **Null Hypothesis (H₀):** Conversion rates are equal
- **Alternative Hypothesis (H₁):** Conversion rates are different

```{r hypothesis-test}
# Contingency table
table_data <- table(ab_data_clean$group, ab_data_clean$converted)

# Proportion z-test
test_result <- prop.test(table_data)
tidy(test_result)
```

## ✅ Interpretation

- **p-value:** 
p = 0.1918 > 0.05
- 
**Conclusion:**  
We fail to reject the null hypothesis. There is no statistically significant difference.
The difference in conversion rates between the control and treatment groups is likely due to random chance, not the new landing page.

## 💼 Business Recommendation

Stick with the current (old) landing page.
Launching the new version likely won't improve business performance, and may not justify design or development costs.

---

## 📎 Summary

**Tools Used:** R, dplyr, ggplot2  
**Test:** 2-proportion z-test  
**Decision:** Data-driven conclusion based on user behavior

```
